FraCaS: 80 percent complete

### 2019-01-18 paper2018/paper.tex
typography

\todo{rejected and changed cases in FraCaS}
\providecommand\forcecenter{\multicolumn{1}{c}}
\begin{table}
  \centering
\begin{tabular}{rlrrrrrr}
  & Section      & \# examples & Ours      & FraCoq & MINE & Nut  & Langpro  \\ \hline
1 & Quantifiers  & 75          & .96 (74)  & .96    & .77  & .53  & .93 (44) \\
2 & Plurals      & 33          & .82       & .76    & .67  & .52  & .73 (24) \\
3 & Anaphora     & 28          & .86       &   -    & -    & -    &  -       \\
4 & Ellipsis     & 52          & .87       &   -    & -    & -    &  -       \\
5 & Adjectives   & 22          & .95 (20)  & .95    & .68  & .32  & .73 (12) \\
6 & Comparatives & 31          & .87       & .56    & .48  & .45  &  -       \\
8 & Verbs        & 8           & .75       &   -    & -    & -    &  -       \\
9 & Attitudes    & 13          & .92       & .85    & .77  & .46  & .92 (9)  \\ \hline
  & Total        & 262         & .89 (259) & .83    & .69  & .50  & .85 (89)
  \end{tabular}
  \caption{Overview of the accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of examples shown in the
    third column, the actual number of examples attempted is shown in
    parentheses.  ``FraCoq'' refers to the work of
    \citet{bernardy_type_2017}. ``MINE" refers to the approach of
    \citet{Mineshima:2015}, ``NUT" to the CCG system that utilizes the
    first-order automated theorem prover \textit{nutcracker} described
    by \citet{bos:2008}, and ``Langpro" to the system presented by
    \citet{Abzianidze:2015}.  }
\end{table}

>>>>

\todo{rejected and changed cases in FraCaS}
\providecommand\forcecenter{\multicolumn{1}{c}}
\begin{table}
  \centering
\begin{tabular}{rlrrrrrr}
  & Section      & \# examples & Ours     & FraCoq & MINE & Nut  & Langpro  \\ \hline
1 & Quantifiers  & 75          & .96 (74) & .96    & .77  & .53  & .93 (44) \\
2 & Plurals      & 33          & .82      & .76    & .67  & .52  & .73 (24) \\
3 & Anaphora     & 28          & .86      &   -    & -    & -    &  -       \\
4 & Ellipsis     & 52          & .87      &   -    & -    & -    &  -       \\
5 & Adjectives   & 22          & .95 (20) & .95    & .68  & .32  & .73 (12) \\
6 & Comparatives & 31          & .87      & .56    & .48  & .45  &  -       \\
8 & Verbs        & 8           & .75      &   -    & -    & -    &  -       \\
9 & Attitudes    & 13          & .92      & .85    & .77  & .46  & .92 (9)  \\ \hline
  & Total        & 262         & .89      & .83    & .69  & .50  & .85  \\
  &              &             & (259)    & (174)  & (174)& (174)& (89)
  \end{tabular}
  \caption{Overview of the accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of examples shown in the
    third column, the actual number of examples attempted is shown in
    parentheses.  ``FraCoq'' refers to the work of
    \citet{bernardy_type_2017}. ``MINE" refers to the approach of
    \citet{Mineshima:2015}, ``NUT" to the CCG system that utilizes the
    first-order automated theorem prover \textit{nutcracker} described
    by \citet{bos:2008}, and ``Langpro" to the system presented by
    \citet{Abzianidze:2015}.  }
\end{table}
